### 2019-11-22 thesis.tex
before moving the solar physics appendix

Collisional interactions are the central point of the present thesis.
However, the formalism presented in \Cref{noneigenmode}, departs from
the weak turbulence equations, which are the nonlinear approximation of
the kinetic equations for low-amplitude instabilities in a collisionless
plasma. The contribution of the correlations between \emph{source}
fluctuations, that account for collisional interactions  (see.~\cite{
  klimon,Tigik2015}), are then retrieved by the inclusion of noneigenmode
contribution in both wave and particle kinetic equations. The difference
of this new approach is that

%% ~\cite{klimon,Tigik2015}

\section{The Vlasov approach}
\label{vlasov-appro}
Collisional interactions can be neglected when the time necessary for
the plasma to establish statistical equilibrium is much greater than the
characteristic time of the process being studied. In this section, we
present a brief discussion about the necessary set of assumptions that
allow us to disregard the effect of collisions in dilute plasmas. In the
sequence we present the complete set of self-consistent equations for
a collisionless plasma.

% Let $\tau_{\rm rel}$ be the time necessary for the plasma to establish
% statistical equilibrium, i.e, the relaxation time.

the relaxation time $\tau_{\rm rel}$ 
% The relaxation time of a plasma is defined
% as follows $\tau_{\rm rel}=\lambda_{De}/v_{th}g$, where $\lambda_{De}$ is
% given by Eq. \eqref{debye}, $v_{th}$ is the thermal velocity, and $g$
% is the plasma parameter.

As mentioned before, in the absence of collisions, the plasma dynamics is given
by the Vlasov-Maxwell system, which is composed of the Vlasov movement equation
\begin{equation}
  \label{eq:vlasov}
  \frac{\partial f_{\alpha}({\bf r},{\bf v},t)}{\partial t}
  +{\bf v \cdot \nabla_r}f_{\alpha}({\bf r},{\bf v},t)
  +\frac{\bf F}{m_{\alpha}}
  {\bf \cdot \nabla_v}f_{\alpha}({\bf r},{\bf v},t)=0.
\end{equation}

@@

>>>>

Collisional interactions are the central point of the present thesis. However,
the formalism presented in \Cref{noneigenmode}, departs from the weak turbulence
equations, which are the kinetic description of nonlinear, low-amplitude
instabilities in a collisionless plasma. The contribution of the correlations
between \emph{source} fluctuations, which account for collisional interactions
(see.~\cite{klimon,Tigik2015}), are then retrieved with the inclusion of
noneigenmode contributions in the wave and particle kinetic equations\footnote{
  For instance, in \Cref{sec:inc-non}, it will be shown that including the
  noneigenmode fluctuations in the weak turbulence's formal particle kinetic
  equation leads to an expression that accounts for the collisional interactions
  that appear on the right-hand side of equation~\eqref{boltz}.}. Therefore,
at this point, it will be assumed that collisions can be neglected.

%% ~\cite{klimon,Tigik2015}
\section{The Vlasov-Maxwell system of equations}
% \label{vlasov-appro}
% When the time necessary for the plasma to establish statistical equilibrium
% is much greater than the characteristic time of the process being studied,
% collisions can be neglected. In this section, is presented a brief discussion
% about the necessary set of assumptions that allow us to disregard the effect
% of collisions in dilute plasmas. In the sequence we present the complete set
% of self-consistent equations for a collisionless plasma.

% \subsection{Plasma parameter and relaxation time}
% \label{plasma-param-relax}
% A plasma is considered diluted when the plasma parameter $g\ll 1$, which
% has the following form
% \begin{equation}
%   \label{ppar}
%   g=\frac{1}{n\lambda_{De}^3},
% \end{equation}
% where $n$ is the number of charges inside the Debye sphere, and $\lambda_{De}$
% is the Debye length, given by Eq. \eqref{debye}. At priory, the inequality
% $g\ll 1$ seems counter intuitive, since it means that you must have a large
% number of charged particles in the Debye sphere. However, if one substitutes
% $\lambda_{De}$ with its expression,
% \begin{align}
%   g&=\frac{4\pi n e^2}{n T_e}\sqrt{\frac{4\pi n e^2}{T_e}}\\
%    &=\frac{4\pi e^2}{T_e}\sqrt{\frac{4\pi n e^2}{T_e}}
% \end{align}

% % Let $\tau_{\rm rel}$ be the time necessary for the plasma to establish
% % statistical equilibrium, i.e, the relaxation time.

% the relaxation time $\tau_{\rm rel}$ 
% The relaxation time of a plasma is defined
% as follows $\tau_{\rm rel}=\lambda_{De}/v_{th}g$, where $\lambda_{De}$ is
% given by Eq. \eqref{debye}, $v_{th}$ is the thermal velocity, and $g$
% is the plasma parameter.

In the absence of collisions, the plasma dynamics is given by the Vlasov-Maxwell
system, which is composed of the Vlasov movement equation
\begin{equation}
  \label{eq:vlasov}
  \frac{\partial f_{\alpha}({\bf r},{\bf v},t)}{\partial t}
  +{\bf v \cdot \nabla_r}f_{\alpha}({\bf r},{\bf v},t)
  +\frac{\bf F}{m_{\alpha}}
  {\bf \cdot \nabla_v}f_{\alpha}({\bf r},{\bf v},t)=0.
\end{equation}

@@

% \chapter{Klimontovich formalism}
% \label{app-klimo}
% % The Klimontovich formalism is the basis of 
% % This appendix has the objective to complement important concepts discussed in
% % \Cref{noneigenmode}. 
% % In this appendix I present the standard approach that leads to the well known
% % Balescu-Lenard collision integral. The objective here is to put the formalism
% % presented in this thesis in a context where it can be compared with the usual
% % text-book method that employs the Klimontovich statistical formulation. The
% % derivation shown here is basically a version of Chapter 4

% \chapter{Microscopic equations for a fully ionized plasma}
% \label{mic-eq}
% Let us consider a fully ionized hydrogen plasma, where $e_a$ and $m_a$ are,
% respectively the charge and the mass of the particles of species $a$, that
% can be or electrons $e_e\equiv -e$ or protons (ions) $e_i\equiv e$. Denoting
% $N_a$ as the total number of particles of species $a$ in the plasma, the
% neutrality condition of a plasma is given by
% \begin{equation}
%   \sum_ae_aN_a=0.  
% \end{equation}

% The probability distribution function for a N-body system in phase-space,
% $({\bf r, v})$, is given by the Klimontovich function
% \begin{equation}
% N_a({\bf r, v}, t)=\sum_{i=1}^{N_a}
% \delta[{\bf r}-{\bf r}_i^a(t)]
% \delta[{\bf v}-{\bf v}_i^a(t)],
% \end{equation}
% where ${\bf r}_i^a$ is the exact position and ${\bf v}_i^a$ the exact velocity
% of the $i\unit{th}$ particle of species $a$, in a given time $t$.
